Using spatially biased variables in ecosystem condition accounting with a GIS based workflow

### 2024-02-23 manuscript/HIAs.qmd
sample size in forest plot

```{r forets plot}
# Forest plot
# https://stackoverflow.com/questions/58657802/forest-plot-with-subgroups-in-ggplot2
```

>>>>

```{r forets plot}
# Forest plot
# https://stackoverflow.com/questions/58657802/forest-plot-with-subgroups-in-ggplot2
# 
# #define colours for dots and bars
dotCOLS = c("grey90","grey70", "grey50", "grey40")

barCOLS <- tmaptools::get_brewer_pal("Set1", n = 4)
#barCOLS = c("grey80","grey60", "grey40", "grey20")

stats_tbl |>
  mutate(
    indicator = case_when(
      indicator == "i_ADSV" ~ "ADSV",
      indicator == "i_alien" ~ "Alien species",
      indicator == "i_ditch" ~ "Trenching"
    )
  ) |>
  ggplot(aes(x=infrastructureIndex, 
             y=mean, 
             ymin=mean-sd, 
             ymax=mean+sd,
             col=factor(infrastructureIndex),
             fill=factor(infrastructureIndex))) + 
#specify position here
  geom_linerange(
    size=10,
    #position=position_dodge(width = .9)
    ) +
  #geom_hline(yintercept=1, lty=2) +
#specify position here too
  geom_point(
    size=3, 
    shape=21, 
    colour="white", 
    stroke = 0.5,
    #position=position_dodge(width = .9)
    ) +
  geom_text(
    aes(y = mean-sd, label = n),
    nudge_y = -0.1,
    show.legend = F
  ) +
  scale_fill_manual(values=dotCOLS)+
  scale_color_manual(values=barCOLS)+
  scale_x_discrete(name="") +
  scale_y_continuous(name="Indicator values", limits = c(0, 1)) +
  coord_flip() +
  theme_bw() +
  labs(fill = "HIA",
       col = "HIA") +
  facet_grid(indicator ~ Municipality)
```
